---
title: "Provider Report"
output: html_document
params:
  provider: "Dr. Cox"
  visit_reason: "sports_injury"
---

```{r setup, include = F}
library(dplyr)
library(ggplot2)
library(highcharter)
library(lubridate)
library(magrittr)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

Dear `r params$provider`,

Thank you for your recent investment in tracking patients' length of stay.  Please see the below visualization for this project's main metric.

```{r dataset}
dataset <- readr::read_csv("dataset.csv")
```

```{r los_heatmap}
dataset <- dataset %>%
  mutate(discharge_month = floor_date(hosp_discharge_dt, "month")) %>%
  filter(provider == params$provider)
  
los_heatmap_data <- dataset %>%
  group_by(discharge_month, visit_reason) %>%
  summarise(mean_los = mean(los_hours / 24)) %>%
  ungroup()

ggplot(los_heatmap_data, aes(x = as.Date(discharge_month), y = visit_reason)) +
  geom_tile(aes(fill = mean_los),
            colour = "white") +
  scale_fill_gradient(low = "white",
                      high = "steelblue") +
  xlab("Discharge Month") +
  scale_x_date(date_breaks = "1 month", date_labels = "%b %Y") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylab("Visit Condition") +
  labs(fill = "LOS Days")
```

```{r last_month_los}
last_month_los_highest <- los_heatmap_data %>% 
  filter(discharge_month == floor_date(Sys.Date() %m-% months(1), "month")) %>% 
  arrange(desc(mean_los)) %>% 
  select(visit_reason) %>% 
  slice(1) %>% 
  as.character()
```

For the past month, the patient population with the longest length of stay that you cared for was **`r last_month_los_highest`**.

The following graphs shows the arrival times for patients with **`r params$visit_reason`**, split by weekends and weekdays.

```{r minutes_midnight}
minutes_midnight_data <- dataset %>% 
  filter(visit_reason == params$visit_reason) %>%
  mutate(admit_month = floor_date(hosp_admit_dt, "month"),
         weekend_weekday = case_when(admit_dow %in% c("Sat", "Sun") ~ "Weekend",
                                     TRUE ~ "Weekday")) %>% 
  group_by(weekend_weekday, admit_month) %>% 
  summarize(mean_hours = mean(minutes_since_midnight)/60) %>% 
  ungroup()

# Split between weekends and weekdays
minutes_midnight_data_weekday <- filter(minutes_midnight_data, 
                                        weekend_weekday == "Weekday")

minutes_midnight_data_weekend <- filter(minutes_midnight_data, 
                                        weekend_weekday == "Weekend")

# Visualize
highchart(type = "stock") %>%
  hc_add_series(minutes_midnight_data_weekday,
                name = "Weekday Minutes",
                type = "line",
                marker = list(enabled = T, symbol = "circle", radius = 3),
                hcaes(x = as.Date(admit_month), y = mean_hours)) %>%
  hc_add_series(minutes_midnight_data_weekend,
                name = "Weekend Minutes",
                type = "line",
                marker = list(enabled = T, symbol = "circle", radius = 3),
                hcaes(x = as.Date(admit_month), y = mean_hours))
```

Best,

The Clinical Quality Team